Larkin Secondary CREP

### 2023-09-18 manuscript/manuscript.Rmd
fixing links to data
updating with names of authors

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

@@

```{r}
# import data 
load("full_long.Rdata")

>>>>

author:
  - name: Kaitlyn Larkin
    affiliation: '1'
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Project administration
      - Writing - original draft
      - Writing - review & editing
    email: kaitlynalarkin@outlook.com
  - name: Michael R. Andreychik
    affiliation: '1'
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Project administration
      - Supervision
      - Writing - original draft
      - Writing - review & editing
    corresponding: yes
    email: mandreychik@fairfield.edu
    address: Enter postal address here
  - name: Sophia Weissgerber
    affiliation: '2'
    role:
      - Investigation
      - Software
      - Supervision
      - Writing - review & editing
    email: scweissgerber@uni-kassel.de
  - name: Felix Kiunke
    affiliation: '2'
    role:
      - Data curation
      - Investigation
      - Software
      - Writing - review & editing
    email: mail@fkiunke.de
  - name: Hendrik Godbersen
    affiliation: '3'
    role:
      - Investigation
      - Writing - review & editing
    email: hendrik.godbersen@fom.de
  - name: Caroline Kolle
    affiliation: '2'
    role:
      - Investigation
      - Writing - review & editing
    email: Caroline.Kolle@gmx.de
  - name: Anna Kulpe
    affiliation: '2'
    role:
      - Investigation
      - Writing - review & editing
    email: anna.kulpe@web.de
  - name: Susana Ruiz-Fernandez
    affiliation: '4,8'
    role:
      - Investigation
      - Supervision
      - Writing - review & editing
    email: susana.ruiz-fernandez@psychology-research.de
  - name: Kaitlyn M. Werner
    affiliation: '5'
    role:
      - Investigation
      - Supervision
      - Writing - review & editing
    email: kaitlyn.werner@utoronto.ca
  - name: Raymond Wu
    affiliation: '6'
    role:
      - Investigation
      - Writing - review & editing
    email: rwu@psych.ubc.ca
  - name: Erin M. Buchanan
    affiliation: '7'
    role:
      - Data curation
      - Formal analysis
      - Software
      - Validation
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    email: ebuchanan@harrisburgu.edu

affiliation:
  - id: '1'
    institution: Fairfield University
  - id: '2'
    institution: University of Kassel
  - id: '3'
    institution: FOM University of Applied Sciences, Essen, Germany
  - id: '4'
    institution: Brandenburg University of Technology, Cottbus-Senftenberg, Germany
  - id: '5'
    institution: University of Toronto
  - id: '6'
    institution: University of British Columbia
  - id: '7'
    institution: Harrisburg University of Science and Technology
  - id: '8'
    institution: FOM University of Applied Sciences, Essen; Leibniz Institut für Wissensmedien,
      Tübingen, Germany

@@

```{r}
# import data 
load("../data/full_long.Rdata")
